---
title: "Excercise2"
author: "Atte Koskivaara"
---
rm(list=ls())
# Regression and model validation


Here we read the table with following headers: "gender"   "Age"      "Attitude" "deep"     "stra"     "surf"    
"Points"

```{r}
learning14 <- read.table("C:/Users/user1/Documents/GitHub/IODS-project/data/learning2014.csv", sep=",", header=TRUE)
str(learning14)
colnames(learning14)

```
```{r}
library(ggplot2)
p1 <- ggplot(learning14, aes(x = Attitude, y = Points, col = gender))

p2 <- p1 + geom_point()

p2

p3 <- p2 + geom_smooth(method = "lm")

p4 <- p3+ggtitle("Student's attitude versus exam points")
p4


```


Students' attitude and test performance seem to have a high correlation. Also, female students group is about twice as big as male group.

```{r}

pairs(learning14[-1], col = learning14$gender)

library(GGally)
library(ggplot2)

p <- ggpairs(learning14, mapping = aes(col=gender, alpha = 0.3), lower = list(combo = wrap("facethist", bins = 20)))

p


```
```{r}

ggpairs(learning14, lower = list(combo = wrap("facethist", bins = 20)))


my_model2 <- lm(Points ~ Attitude + gender + Age, data = learning14)

summary(my_model2)


```
Gender and age does not have a statististically significant relationship, thus we can leave them out from the model.







